---
title: "Madhu_Lab1"
author: "Madhu Jagdale"
date: "2/3/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---
### 2. Hello World!

#### Here’s an R code chunk that prints the text ‘Hello world!'
```{r}
print("Hello World!")
```
#### (a) Modify the code chunk below to print your name
```{r}
print("Madhu Jagdale")
```


### 3. Creating sequences
#### Using Colon operator
```{r}
1:10  # Numbers 1 to 10
127:132 # Numbers 127 to 132
```
#### Using seq function: seq(from, to, by)
```{r}
seq(1,10,1) # Numbers 1 to 10
seq(1,10,2) # Odd numbers from 1 to 10
seq(2,10,2) # Even numbers from 2 to 10

```
#### (a) Use : to output the sequence of numbers from 3 to 12
```{r}
3:12
```
#### (b) Use seq() to output the sequence of numbers from 3 to 30 in increments of 3
```{r}
seq(3,30,3)
print("Hi")
```
#### (c) Save the sequence from (a) as a variable x, and the sequence from (b) as a variable y. Output their product x*y
```{r}
x<- 3:12
y<- seq(3,30,3)
x*y
```
### 4. Cars data
```{r}
head(cars)
```
#### By Using the attach() command, which will allow us to access the speed and dist columns of cars as though they were vectors in our workspace.
```{r}
attach(cars)
speed
dist
```
#### (a) Calculate the average and standard deviation of speed and distance.
```{r}

mean(speed)
mean(dist)
sd(speed)
sd(dist)
```
### 5. Histogram and Scatterplot
#### (a) Produce a histogram of stopping distance using the qplot function.
```{r}
library(ggplot2)
qplot(dist) # Histogram of stopping distance
```

#### (b)Use the qplot(x,y) function to create a scatterplot of dist against speed.

```{r}


library(ggplot2)
ggplot(cars,aes(x=speed,y=dist))+geom_point()  #Scatterplot of dist against speed.



```








